Untitled

### 2023-02-10 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
Update on supp mat

output: 
  pdf_document:
    extra_dependencies: ["float"]
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{float}
- \usepackage{caption}
- \usepackage{setspace}\doublespacing
- \usepackage{soul}
- \floatplacement{figure}{H}
- \usepackage{afterpage}
- \usepackage{placeins}
- \usepackage{graphicx}
- \usepackage{floatpag}

@@

```{r echo=FALSE,warning=FALSE}
knitr::opts_chunk$set(fig.pos = "h", out.extra = "")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.", fig.pos= "h"}

>>>>

output: 
  pdf_document:
    extra_dependencies: ["float"]
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{float}
- \usepackage{caption}
- \usepackage{setspace}\doublespacing
- \usepackage{soul}
- \usepackage{afterpage}
- \usepackage{placeins}
- \usepackage{graphicx}
- \usepackage{floatpag}

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics."}
